---
title: "BNB-Price-Prediction-Project"
author: "Shrey Jaradi"
date: "2022-11-23"
output: html_document
---

```{r}
library('dplyr')
library('lubridate')
library('tidyverse')
library('ggplot2')
```


```{r}
bnb_df = read.csv(file='../data/AB_NYC_2019.csv') 
head(bnb_df)
```
```{r}
dim(bnb_df)
```
```{r}
summary.default(bnb_df)
```

**name :** Name of the Place 
**host_name :** It's a host name - name of owner  - not much important          
**neighbourhood_group :** This also we can convert to dummy variable -as this is also important- there are certain negihbourhood where price is varies  
**neighbourhood :** There are so many values if we create dummy variable for this, it's gonna create so much feature better to ignore this column            
**Room Type :**  we can convert to Dummy variable as there are three Room Type and it will help us as this is much relevant column 
**last_review  :** This is date column we can convert it to datetime column. 

```{r}
cat("Room Type : ", unique(bnb_df$room_type))
cat("\nNeighbourhood group : ",unique(bnb_df$neighbourhood_group))
```
 
Let's try to understand the statistics by Room Type , As we are trying to predict price , Let's check what are the minimum, maximum, average price according to room type and neighbourhood group

Manhattan is costliest area, their average price is almoot $250.
```{r}
options(dplyr.summarise.inform = FALSE)
bnb_df %>% group_by(room_type, neighbourhood_group) %>% dplyr::summarise(min_price = min(price), avg_price = mean(price),max_price = max(price))
```
 
```{r}

```

 

